\documentclass[prb]{revtex4}
\usepackage{amsmath}
\begin{document}

\section{Collocate}\label{sec:collocate}
We want to compute the density matrix starting of a quantum state
$\left|\phi\right>$ decomposed on a gaussian basis set (not necessary orthogonal
basis). the over of the basis set is regrouped in product of two gaussians with
parameter $\eta_1$ and $\eta_2$ that are centered around two points ${\bf r}_1$
and ${\bf r}_2$ in real space. Moreover the summation involves sum over angular
momentums $l_i\in\left[l_{\sf min}^i, l_{\sf max}^i\right]$ with $i=1,2$ ($i$ is
not a exponent here). The contribution of this group of gaussians multiplied by
the cartesians harmonics to the density is given by
\begin{equation}
  \label{eq:collocate:1}
  n(x,y,z) = \sum_{l_1 = l_{min}^1}^{l_{max}^1} \sum_{l_1 = l_{min}^2}^{l_{max}^2} \sum_{\substack{\alpha_1 + \beta_1 + \gamma_1 = l_1\\\alpha_2 + \beta_2 + \gamma_2 = l_2}} C^{l_1,l_2}_{\alpha\beta\gamma} (x-x_1)^{\alpha_1} (x-x_2)^{\alpha_2}(y-y_1)^{\beta_1} (y-y_2)^{\beta_2}(z-z_1)^{\gamma_1} (z-z_2)^{\gamma_2} \exp_a\exp_b
\end{equation}
where $C^{l_1,l_2}_{\alpha\beta\gamma}$ and the weights of each individual
gaussian in $\left|\phi\right>$ and $\alpha=(\alpha_1,\alpha_2)$,
$\beta=(\beta_1,\beta_2)$, $\gamma=(\gamma_1,\gamma_2)$. The exponents
$\alpha_i,\beta_i,\beta_i$ are constrained by the following relations
\begin{eqnarray}
  \label{eq:collocate:2a}
  l1 &=& \alpha_1 + \beta_1 + \gamma_1\\
  \label{eq:collocate:2b}
  l2 &=& \alpha_2 + \beta_2 + \gamma_2
\end{eqnarray}
The number of solutions is given by $1, 3, 6, 10, 15, 21, 28, 36, 45, 55, 66$
for $l_1 = 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10$.

Evaluating Eq.\ref{eq:collocate:1} for a fixed $l_1 = 2$, $l_2 = 3$ for instance requires
$60$ possible values of $(\alpha_1,\beta_1,\gamma_1,\alpha_2,\beta_2,\gamma_2)$
(fma operations) times the number of grid points we need to evaluate the
polynomial (periodic boundaries conditions are neglected here). Although it is
easily parallizable, it requires 60 accesses to the density grid. If $l_1$,
$l_2$ covers an interval, all of this adds up which means it is unpractical to
do the summation the brute force way.

\subsection{Orthorombic lattices}
One method to compute Eq.\ref{eq:collocate:1} is to use the fact that the
product of two gaussians is a gaussian of width $\eta_{12} =
\eta_1\eta_2/(\eta_1 + \eta_2)$ centered around ${\bf r}_{12} = (\eta_1 {\bf
  r}_1 + \eta_2 {\bf r}_2)/ (\eta_1 + \eta_2)$ with a weight that depends only
on $\eta_1,\eta_2,{\bf r}_1,{\bf r}_2$.

Instead of evaluating Eq.1 the brute force way, we express the product of
polynomials $(x-x_1)^{\alpha_1} (x-x_2)^{\alpha_2}$ as
\begin{equation}
  \label{eq:collocate:3}
  (x-x_1)^{\alpha_1} (x-x_2)^{\alpha_2} = \sum_{k}^{\alpha_1}\sum_{k'}^{\alpha_2}
  \left(
  \begin{array}{c}
    \alpha_1\\
    k
  \end{array}
  \right)
  \left(
  \begin{array}{c}
    \alpha_2\\
    k'
  \end{array}
  \right)
  (x-x_{12})^k (x_{12} - x_1)^{\alpha_1 - k}  (x_{12} - x_2)^{\alpha_2 - k'}
\end{equation}
where $\left(
\begin{array}{c}
  n\\
  k
\end{array}
\right)$ is the binomial coefficient.

If we apply this to Eq.\ref{eq:1} in all three directions, we obtain
\begin{eqnarray}
  \label{eq:collocate:4}
  n(x,y,z)  &=&
            \sum_{l_1 = l_{\sf min}^1}^{l_{\sf max}^1} \sum_{l_1 = l_{\sf min}^2}^{l_{\sf max}^2} \sum_{\alpha_1,\alpha_2}^{l_1,l_2} \sum_{\substack{\beta_1 = 0\\\beta_2 = 0}} ^{\substack{l_1 - \alpha_1\\l_2 - \alpha_2}}  C^{l_1,l_2}_{\alpha\beta\gamma} \sum_{k_0} ^ {\alpha_1}\sum_{k_1} ^ {\alpha_2} \left(
            \begin{array}{c}
              {\alpha_1}\\
              k_0\end{array}
              \right)
              \left(
              \begin{array}{c}
                \alpha_2\\
                k_1
              \end{array}\right)
              \left(\begin{array}{c}
                \beta_1\\
                k_2\end{array}
                \right)
                \left(
                \begin{array}{c}
                  \beta_2\\
                  k_3
                \end{array}\right)
                \left(\begin{array}{c}
                  l_1 - \beta_1 - \alpha_1\\
                  k_4\end{array}
                  \right)
                  \left(
                  \begin{array}{c}
                    l_2 - \beta_2 - \alpha_2\\
                    k_5
                  \end{array}\right)\nonumber\\ &\times&
                  (x-x_{ab})^{k_0+k_1} (y-y_{ab})^{k_2+k_3} (z - z_{ab}) ^ {k_4 + k_5}\nonumber\\ &\times& (z_{ab} - z_a) ^{l_1 - \beta_1 - \alpha_1 - k_4} (z_{ab} - z_b)^{l_2 - \alpha_2 - \beta_2-k_5}\nonumber  \\ &\times& (y_{ab} - y_a) ^{\beta_1 - k_2} (y_{ab} - y_b)^{\beta_2-k_3}\nonumber \\ &\times& (x_{ab}-x_a)^{\alpha_1 - k} (x_{ab}-x_b)^{\alpha_2 - k'} \exp_a\exp_b
\end{eqnarray}
The advantage is that Eq.\ref{eq:2} only contains monomials of the form
$(x-x_{12}) (y-y_{12}) (z-z_{12})$ with possibly different powers. For instance
for $l_1 = 2$, $l_2 = 3$ (only one pair) we have $46$ monomials instead of $60$.

Now if $l_1, l_2$ covers some range $l_1\in \left[0, 2\right]$, $l_2\in \left[0,
  3\right]$, we obtain an expression with the same number of monomials instead
of $200$. We already have a factor 4 at least between this approach and the
brute force approach.

In discrete form and for the orthorombic case, Eq.\ref{eq:2} can be written as a
matrix-matrix product (actually a tensor - tensor product)
\begin{equation}
  \label{eq:collocate:5}
  n_{ijk} = \sum_{l = 0}^{l^1_{\sf max} + l^2_{\sf max}}  A_{\alpha\beta\gamma} X_{\alpha i} Y_{\beta j} Z_{\gamma k},
\end{equation}
with
\begin{eqnarray}
  \label{eq:collocate:6a}
  X_{i\alpha} &=& (x_i - x_{12})^\alpha \exp(-\eta_{12} (x_i-x_{12})^2)\\
  \label{eq:collocate:6b}
  Y_{j\beta} &=& (y_j - x_{12})^\beta \exp(-\eta_{12} (y_j - y_{12})^2)\\
  \label{eq:collocate:6c}
  Z_{k\gamma} &=& (z_k - z_{12})^\gamma \exp(-\eta_{12} (z_k-z_{12})^2),
\end{eqnarray}
with
\begin{eqnarray}
  \label{eq:collocate:7}
  A_{\alpha\beta\gamma} &=&\left.\frac{\partial^{\alpha+\beta+\gamma} n({\bf
      r})}{\partial^\alpha x \partial ^ \beta y \partial ^ \gamma z} (x - x_{12})^\alpha (y - y_{12})^\beta (z_k -z_{12})^\gamma\right|_{r=r_{12}},\\
  &=&  \sum_{l_1 = l_{\sf min}^1}^{l_{\sf max}^1} \sum_{l_1 = l_{\sf min}^2}^{l_{\sf max}^2} \sum_{\alpha_1 + \alpha_2 = \alpha}^{\substack{\alpha_1 \leq l_1\\ \alpha_2 \leq l_2}} \sum_{\substack{\beta_1 = 0\\\beta_2 = 0}} ^{\substack{l_1 - \alpha_1\\l_2 - \alpha_2}}  C^{l_1,l_2}_{\alpha\beta\gamma} \sum_{k_0} ^ {\alpha_1}\sum_{k_1} ^ {\alpha_2} \left(
            \begin{array}{c}
              {\alpha_1}\\
              k_0\end{array}
              \right)
              \left(
              \begin{array}{c}
                \alpha_2\\
                k_1
              \end{array}\right)
              \left(\begin{array}{c}
                \beta_1\\
                k_2\end{array}
                \right)
                \left(
                \begin{array}{c}
                  \beta_2\\
                  k_3
                \end{array}\right)
                \left(\begin{array}{c}
                  l_1 - \beta_1 - \alpha_1\\
                  k_4\end{array}
                  \right)
                  \left(
                  \begin{array}{c}
                    l_2 - \beta_2 - \alpha_2\\
                    k_5
                  \end{array}\right)\nonumber\\ &\times&
                  (y_j-y_{ab})^{k_2+k_3} (z_k - z_{ab}) ^ {k_4 + k_5}\nonumber\\ &\times& (z_{ab} - z_a) ^{l_1 - \beta_1 - \alpha_1 - k_4} (z_{ab} - z_b)^{l_2 - \alpha_2 - \beta_2-k_5}\nonumber  \\ &\times& (y_{ab} - y_a) ^{\beta_1 - k_2} (y_{ab} - y_b)^{\beta_2-k_3}\nonumber \\ &\times& (x_{ab}-x_a)^{\alpha_1 - k} (x_{ab}-x_b)^{\alpha_2 - k'} \exp_a\exp_b
\end{eqnarray}
taking all terms $k_1 + k_2 = \alpha$ $k_3 + k_4 = \beta$ and $k_5 + k_6 =
\beta$ with $k_1 \leq l^1_{\sf max}$ and $k_2 \leq l^2_{\sf max}$ in
Eq.\ref{eq:3}.

$n_{ijk}$ can be evaluated with tensor-tensor products which reduces to matrix -
matrix products. The matrix products are evaluated the following way
\begin{equation}
  \label{eq:collocate:8}
  T^1_{\alpha\beta k} = \sum_{\gamma} A_{(\alpha\beta)\gamma} Z_{\gamma, k}
\end{equation}
the $(\alpha\beta)$ notation indicating that we treat it a composite indice. Then
\begin{equation}
  \label{eq:collocate:9}
  T^2_{\alpha j k} = \sum_{\beta} T^1_{\alpha k \beta} Y_{\beta, j}
\end{equation}
where we need to transpose the second and third indices of $T^1$ and finally
\begin{equation}
  \label{eq:collocate:10}
  n_{ijk} = \sum_{\alpha} X_{\alpha, i} ^T T^2_{\alpha (j k)}
\end{equation}

\subsection{Non orthorombic lattices}
Evaluating the density operator on a non orthorombic lattice or grid requires a
priori to evaluate all polynomials for each point of the grid if we use
Eq.\ref{eq:1}. However, it is possible to recast Eq.\ref{eq:1} for non
orthorombic lattices into a problem that has a structure that is similar to the
orthorombic case.

We suppose the grid regular in the basis formed by the displacement vectors of
the lattice. We will write then as $v_1, v_2, v_3$. A grid point $ijk$ will have
the following cartesian coordinates
\begin{equation}
  \label{eq:collocate:11}
  {\bf r}_{ijk} = (x_i, y_j, z_k) = i {\bf v}_1 + j {\bf v}_2 + k {\bf v}_3
\end{equation}
$x_i, y_j, z_k$ can be obtained after projection along $x,y,z$. The point is
that we can replace the cartesian coordinates by their expression in
Eq.\ref{eq:2}. We will obtain formula of this type
\begin{equation}
  \label{eq:collocate:12}
  n_{ijk} = \sum_{\alpha\beta\gamma}  A_{\alpha\beta\gamma} I_{\alpha i} J_{\beta j} K_{\gamma k} {\sf Exp}_{ij} {\sf Exp}_{jk} {\sf Exp}_{ik},
\end{equation}
where
\begin{eqnarray}
  \label{eq:collocate:13a}
  X_{i\alpha} &=& (i - x'_{12})^\alpha \exp(-\eta_{12} (i ^ 2 (v_1)^2 - x'_{12})^2)\\
  Y_{j\beta} &=& (j - y'_{12})^\beta \exp(-\eta_{12} (j ^ 2 (v_2)^2 - y'_{12})^2)  \label{eq:collocate:13b}
\\
Z_{k\gamma} &=& (k - z'_{12})^\gamma \exp(-\eta_{12} (k^2 (v_3)^2 - z'_{12})^2)  \label{eq:collocate:13c},
\end{eqnarray}
and
\begin{eqnarray}
  \label{eq:collocate:14a}
  {\sf Exp}_{ij} &=& \exp\left(\eta_{12} (v_1 \cdot v_2) (i-x'_{12})(j-y'_{12}) \right)\\
  {\sf Exp}_{jk} &=& \exp\left(\eta_{12} (v_2 \cdot v_3) (j-y'_{12})(k-z'_{12}) \right)  \label{eq:collocate:14b}
\\
  {\sf Exp}_{ik} &=& \exp\left(\eta_{12} (v_1 \cdot v_3) (i-x'_{12})(k-z'_{12}) \right).  \label{eq:collocate:14c}
\end{eqnarray}
If the boundaries conditions are open then it is possible to use the same trick
than for the orthorombic case and then multiply the final result with the
corrections ${\sf Exp}_{ij}$.

When period boundaries conditions are imposed, we have a extra summation over
the period in the dimensions wheren the PBC is imposed. $n_{ijk}$ ($i,j,k$ are
now within the unit cell) becomes
\begin{equation}
  \label{eq:collocate:15}
  n_{ijk} = \sum_{n,m,l} \left(\sum_{\alpha\beta\gamma}
  A_{\alpha\beta\gamma} I_{\alpha, i+m} J_{\beta, j+n} K_{\gamma, {k+l}} {\sf
    Exp}_{i+m, j+n} {\sf Exp}_{j+n, k+l} {\sf Exp}_{i + m, k + l}\right)
\end{equation}
summation over $\alpha\beta\gamma$ can still use the same method than for the
orthorombic case, but we have to repeat the same calculations multiple times to
cover the summation over $n,m,l$.

\section{Integrate routine}

The integrate routine is similar to the collocate routine described in
Sec.\ref{sec:collocate}. The starting point is the evaluation of
\begin{equation}
  \label{eq:integrate:0}
  C_{\alpha\beta\gamma} = \int V({\bf r}) P^{\alpha\beta\gamma}({\bf r}) \exp(- \eta ({\bf r} - {\bf r}_{12})^2)
\end{equation}
on a regular mesh, $\alpha\beta\gamma$ the power of the monomials $x-x_{12}, y -
y_{12}$ and $z-z_{12}$. After discretization, we obtain
\begin{equation}
  \label{eq:integration:1}
  C_{\alpha\beta\gamma} = \sum_{ijk} V_{ijk} (x_i -x_{12})^\alpha (y_j -y_{12})^\beta (z_k - z_{12})^\gamma \exp\left(({\bf r}_{ijk} - {\bf r}_{12})^2\right)
\end{equation}
for $\alpha\beta\gamma$ running over some interval. We have to separate the
orthogonal and non orgothonal grids

\subsection{Orthorombic case}
If the grid is orthorombic then Eq.\ref{eq:integration:1} can be done with
matrix-matrix multiplication. To show the explicit matrix-matrix multiplication,
we use the name notation than in Sec.1, namely
\begin{eqnarray}
  \label{eq:integrate:2}
  X_{\alpha,i} &=& (x_i -x_{12})^\alpha \exp\left( \eta (x_i -x_{12})^2\right)\\
  Y_{\beta,j} &=& (y_j -y_{12})^\alpha \exp\left( \eta (y_j -y_{12})^2\right)\\
  Z_{\gamma,k} &=& (z_k -z_{12})^\alpha \exp\left( \eta (z_k -z_{12})^2\right).
\end{eqnarray}
with these conventions Eq.ref{eq:integration:1} reduces to
\begin{equation}
  C_{\alpha\beta\gamma} = V_{ijk} X_{\alpha,i} Y_{\beta,j} Z_{\gamma,k},
\end{equation}
where we use the summation over repeated indices. We can easily recognize a
series of matrix-matrix products, starting first the summation over $i$.
\begin{eqnarray}
  \label{eq:integrate:3}
  C_{\alpha\beta\gamma} &=& (V_{ijk} X_{\alpha,i}) Y_{\beta,j} Z_{\gamma,k}\\
  &=& (T_{jk\alpha} Y_{\beta,j}) Z_{\gamma,k}\\
  &=& H_{k,\alpha,\beta} Z_{\gamma,k},
\end{eqnarray}
with
\begin{equation}
  \label{eq:integrate:4}
  T_{jk\alpha} = V_{ijk} X_{\alpha,i},
\end{equation}
and
\begin{equation}
  \label{eq:integrate:5}
  H_{k,\alpha,\beta} = T_{jk\alpha} Y_{\beta,j}.
\end{equation}
Periodic boundaries conditions do not impose more constrain since they can be
included during the calculation of the polynomial $P^{\alpha,\beta,\gamma}({\bf
  r})$.

The matrix elements of the potential $V$ between two gaussians multiplied by
their cartesian harmonics can be obtained using the following relation
\begin{equation}
  \label{eq:integrate:6}
  (x-x_{12})^\alpha = 2 ^{-\alpha}\sum_{k=0}^\alpha\sum_{k_1=0}^k\left(
  \begin{array}{c}
    \alpha \\
    k
  \end{array}
  \right)
  \left(
  \begin{array}{c}
    k \\
    k_1
  \end{array}
  \right)
  (2 x_{12} + x_1 + x_2)^{\alpha-k}(x-x_1)^{k_1}(x-x_2)^{k-k_1}.
\end{equation}
With the constrain that $l_1 =\alpha_1+\beta_1+\gamma_1$ and $l_2
=\alpha_2+\beta_2+\gamma_2$, we can compute the matrix elements of the potential
using Eq.\ref{eq:integrate:3} and Eq.\ref{eq:integrate:4}. The cofficient
${\tilde C}_{\alpha_1\alpha_2} (x-x_1)^{\alpha_1} (x-x_2)^{\alpha_2}$ is given
by
\begin{equation}
  {\tilde C}_{\alpha_1\alpha_2}=\sum_{\alpha \leq \max(\alpha_1,\alpha_2)}^{l_1+l_2}2^{-\alpha}
  \left(
  \begin{array}{c}
    \alpha \\
    \alpha_1
  \end{array}\right)\left(
  \begin{array}{c}
    \alpha_1 \\
    \alpha_2
  \end{array}
  \right) C_{\alpha} (2 x_{12} + x_1 + x_2)^{\alpha-\alpha_1}
\end{equation}
it is more tedious to write the formulas than writing the
\subsection{Non orthorombic grids}
We can start from Eq.\ref{eq:integrate:0} for evaluating the matrix elements on
non orthorombic grids. The polynomial can not be calculated as monomials of
cartesian coordinates (i.e. $P=P_xP_yP_z$ with $(x,y,z)\in [a,b]\times [c,d]
\ times [e,f]$) but can still be written as monomials in $x',y',z'$ in the
displacements vectors of the lattice. However the term coming from the
exponential will contains terms of the form $(x'-x'_{12})(y'-y'_{12})$, etc in
the sum over the lattice points. The final expression is then
\begin{equation}
  \label{eq:integration:7}
  C_{\alpha\beta\gamma} = \sum_{ijk} V_{ijk} {\tilde X}_{\alpha,i} {\tilde Y}_{\beta,j} {\tilde Z}_{\gamma,k} {\sf Exp}_{ij}{\sf Exp}_{jk}{\sf Exp}_{ki}
\end{equation}
where ${\tilde X}$ are the polynomials given in\ref{eq:integrate:2} but {\bf
  expressed} in the lattice basis. The matrices $Exp_{ij}$ are given by
Eq.\ref{eq:collocate:5}. It is not possible to compute the summation numerically
with only matrix-matrix product. However, after reorganising terms a bit we arrive to
\begin{eqnarray}
  \label{eq:integration:8}
  C_{\alpha\beta\gamma} &=& \sum_{jk}\left({\sf Exp}_{jk}\sum_{i}{V}_{ijk} {\tilde X}_{\alpha,i} {\sf Exp}_{ij} {\sf Exp}_{ik}\right) {\tilde Z}_{\gamma,k} {\tilde Y}_{\beta,j}\\
  &=& T_{\alpha,j,k} {\tilde Y}_{\beta,j} {\tilde Z}_{\gamma,k},
\end{eqnarray}
with
\begin{equation}
  \label{eq:integration:9}
  T_{\alpha,j,k} ={\sf Exp}_{jk}\sum_{i}V_{ijk} {\tilde X}_{\alpha,i} {\sf Exp}_{ij} {\sf Exp}_{ik}.
\end{equation}
$T_{\alpha,j,k}$ can not be calculated with a matrix matrix product, but with
proper addressing can be reduced to elementwise scalar multiplications, that are
easily vectorizable. The remaining steps can be done with matrix-matrix
multiplication.

Periodic boundaries conditions however need a special treatment. The simplest
way to consider them is to use tiling and treat each image separately.

\subsection{Computing the coefficients in the two gaussian basis}
Evaluating Eq.\ref{eq:integrate:3} is straightforward, but the matrix elements
of the potential $V^{\alpha\beta\gamma}$ are a superposition of the matrix
elements of the potential in the two gaussian basis. To compute them in the
original basis we use the identity
\begin{equation}
  \label{eq:integrate:4}
  (x - x_1)^{\alpha_1}(x - x_2)^{\alpha_2} = \sum_{k1, k_2}^{\alpha_1,\alpha_2} \left(\begin{array}{c}
      \alpha_1\\ k_1
  \end{array}\right)
  \left(
  \begin{array}{c}
    \alpha_2\\ k_2
  \end{array}
  \right)
  (x - x_{12})^{k_1 + k_2} (x_{12} - x_1)^{\alpha_1 - k_1} (x_{12} - x_2)^{\alpha_2 - k_2}.
\end{equation}
The matrix elements of $V({\bf r})$ are then given by
\begin{equation}
  V_{\alpha_1\alpha_2}^{\beta\gamma} = \sum_{k1, k_2}^{\alpha_1,\alpha_2} \left(\begin{array}{c}
    \alpha_1\\ k_1
  \end{array}\right)\left(\begin{array}{c}
    \alpha_2\\ k_2
  \end{array}\right)V^{k_1 + k_2,\beta\gamma} (x_{12} - x_1)^{\alpha_1} (x_{12} - x_2)^{\alpha_2}.
\end{equation}
after repeating the same operation over $\beta$ and $\gamma$ we finally obtain
\begin{eqnarray}
  \label{eq:integrate:5}
  V_{\alpha_1\alpha_2\beta_1\beta_2\gamma_1\gamma_2} &=& \sum_{\substack{k_1 k_2\\
      k_3 k_4\\
      k_5 k_6}}^{\substack{k_1\leq \alpha_1k_2\leq\alpha_2\\
    k_3\leq\beta_1k_4\leq\beta_2\\
    k_5\leq\gamma_1k_6\leq\gamma_2}} \left(\begin{array}{c}
    \alpha_1\\ k_1
  \end{array}\right)\left(\begin{array}{c}
    \alpha_2\\ k_2
  \end{array}\right)\left(\begin{array}{c}
    \beta_1\\ k_3
  \end{array}\right)\left(\begin{array}{c}
    \beta_2\\ k_4
  \end{array}\right)\left(\begin{array}{c}
    \gamma_1\\ k_5
  \end{array}\right)\left(\begin{array}{c}
    \gamma_2\\ k_6
  \end{array}\right)V^{k_1 + k_2,k_3+k_4,k_5+k_6}\nonumber\\
  &\times&  (x_{12} - x_1)^{\alpha_1 - k_1} (x_{12} - x_2)^{\alpha_2 - k_2} \nonumber\\
  &\times& (y_{12} - y_1)^{\beta_1 - k_3} (y_{12} - y_2)^{\beta_2 - k_4} \nonumber\\
  &\times&(z_{12} - z_1)^{\gamma_1 - k_5} (z_{12} - z_2)^{\gamma_2 - k_6}.
\end{eqnarray}
Note that the expression \ref{eq:integrate:5} is also valid for non orthorombic
grids.

\end{document}
